Very simplified likelihood

### 2024-02-12 inst/very_simplified_likelihood.Rmd
alternative f_single()

@@

```{r,label=calcbothlikes,cache=F}
x <- seq(from=0.1,to=0.8,by=0.01)
jj <- as.matrix(expand.grid(x,x))
L <- apply(jj,1,supp2,results$place,results$runners)
L <- L - max(L,na.rm=TRUE)
L <- matrix(L,length(x),length(x))
```

@@

```{r,cache=F}
x <- seq(from=0.1,to=0.95,by=0.01)
jj <- as.matrix(expand.grid(x,x))
L <- apply(jj,1,supp2_ed,rank[wp]-1,rank[wa]-1,class_size[wp]-1,class_size[wa]-1)
L <- L - max(L,na.rm=TRUE)
L <- matrix(L,length(x),length(x))
```

```{r}
par(pty='s')
contour(x,x,L,asp=1,xlim=range(x),ylim=range(x),levels=-(0:5),
xlab='pure strength',ylab='applied strength')
abline(0,1)
```

```{r}
jj1 <- 
optim(
   c(.4,.8),
   function(vec){
      supp2_ed(vec,rank[wp]-1,rank[wa]-1,class_size[wp]-1,class_size[wa]-1)},
   control=list(fnscale = -1)
)
jj1
```

```{r}
jj2 <-
optimize(function(v){supp2_ed(c(v,v),rank[wp]-1,rank[wa]-1,class_size[wp]-1,class_size[wa]-1)},
c(0.1,0.9),maximum=TRUE)
jj2
```

```{r}
pchisq(2*(jj1$value-jj2$objective),lower.tail=FALSE,df=1)
```

>>>>

f_single2 <- function(a,r,n,log=FALSE){  # not vectorised
  B <- 1/(1-a)
  if(log){
     if(r==n){  # last place
       out <- lgamma(B)-lgamma(B+n)
     } else {   # not last
       out <- log(B-1) - lfactorial(B+n-1) + lfactorial(B+n-r-2)
     }
   } else {  # not-log 
     if(r==n){
      out <- gamma(B)/gamma(B+n)
     } else {
       out <- (B-1)/prod(B+(n-r-1):(n-1))
     }
   }	
   return(out)
}

@@

```{r,label=calcbothlikes,cache=TRUE}
x <- seq(from=0.1,to=0.8,by=0.01)
jj <- as.matrix(expand.grid(x,x))
L <- apply(jj,1,supp2,results$place,results$runners)
L <- L - max(L,na.rm=TRUE)
L <- matrix(L,length(x),length(x))
```

@@

```{r,label=fishbish,cache=TRUE}
x <- seq(from=0.1,to=0.95,by=0.01)
jj <- as.matrix(expand.grid(x,x))
L <- apply(jj,1,supp2_ed,rank[wp]-1,rank[wa]-1,class_size[wp]-1,class_size[wa]-1)
L <- L - max(L,na.rm=TRUE)
L <- matrix(L,length(x),length(x))
```

```{r,label=contourstrength}
par(pty='s')
contour(x,x,L,asp=1,xlim=range(x),ylim=range(x),levels=-(0:5),
xlab='pure strength',ylab='applied strength')
abline(0,1)
```

```{r,label=defsupp2}
jj1 <- 
optim(
   c(.4,.8),
   function(vec){
      supp2_ed(vec,rank[wp]-1,rank[wa]-1,class_size[wp]-1,class_size[wa]-1)},
   control=list(fnscale = -1)
)
jj1
```

```{r,label=findmaxlike}
jj2 <-
optimize(function(v){supp2_ed(c(v,v),rank[wp]-1,rank[wa]-1,class_size[wp]-1,class_size[wa]-1)},
c(0.1,0.9),maximum=TRUE)
jj2
```

```{r,label=shochisw}
pchisq(2*(jj1$value-jj2$objective),lower.tail=FALSE,df=1)
```
